---
title: "Data Wrangling (Data Preprocessing)"
author: "Jeremy Jian Zhi Chia"
subtitle: Practical assessment 2
date: "25/09/2021"
output:
  html_notebook: default
  pdf_document: default
  html_document:
    df_print: paged
---


## **Setup**

```{r}

# Load the necessary packages required to reproduce the report. For example:

library(kableExtra)
library(magrittr)
library(dplyr)
library(tidyr)
library(readr)
library(readxl)
library(openxlsx)
library(ggplot2)
library(tools)

```


## **Student names, numbers and percentage of contributions**
```{r, echo=FALSE}

# Add your names, numbers and percentage of your contribution here.

na<- c("Jeremy Jian Zhi Chia")
no<- c("s3917515")
pc<- c("100%")

s<- data.frame(cbind(na,no,pc))
colnames(s)<- c("Student name", "Student number", "Percentage of contribution")

s %>% kbl(caption = "Group information") %>%
  kable_classic(full_width = F, html_font = "Cambria")

```
<br>
<br>

## **Executive Summary**

In your own words, provide a brief summary of the preprocessing. Explain the steps that you have taken to preprocess your data. Write this section last after you have performed all data preprocessing. (Word count Max: 300 words)
You may use bulleted lists like this:

* a
* b
* ....

<br>
<br>

## **Data**
Source 1:
Data Vic (https://discover.data.vic.gov.au/dataset/victorian-property-sales-report-median-house-by-suburb)

Description:
This dataset lists the percentage shift in median prices between quarters as well as the change over a 12-month period for Victorian houses.

Variables:
Suburb - All suburbs in Victoria, Austraalia
Jul-Sep 19 - Median house prices for that period
Oct-Dec 19 - Median house prices for that period
Jan-Mar 20 - Median house prices for that period
Apr-Jun 20 - Median house prices for that period
Jul-Sep 20 - Median house prices for that period
No of Sales Jul-Sep 20 - Number of house sales for that period
No of Sales YTD - Year to date number of house sales
Change % Jul-Sep 19 Jul-Sep 19 - Percentage change in median house price between two periods
Change % Apr-Jun 20 Jul-Sep 20 - Percentage change in median house price between two periods

Source 2: Crime Statistics Agency (https://www.crimestatistics.vic.gov.au/crime-statistics/historical-crime-data/download-data-3)
Description: There are five tables within this excel workbook. 
The datasets of interest are chosen from these five tables:
- The crime rate by principal offence, LGA and police service area dataset
- Criminal incidents by LGA and suburb dataset
- Criminal incidents by charge status and LGA dataset

Variables:


```{r}

# Import the data, provide your R codes here.

# House median prices dataset
house_medians <- read_excel("data/House_Medians3rdQtr2020.xls", skip = 1)

# Crime rate by principal offence, LGA and police service area dataset
crime_rate <- read_excel("data/Data_Tables_LGA_Criminal_Incidents_Year_Ending_September_2020.xlsx%3F8rMGzuMnVt5oC9mV_AAn_dmq1tfyPo9T=.xlsx", 
    sheet = "Table 02")

# Criminal incidents by LGA and suburb dataset
criminal_incidents_lga_suburb <- read_excel("data/Data_Tables_LGA_Criminal_Incidents_Year_Ending_September_2020.xlsx%3F8rMGzuMnVt5oC9mV_AAn_dmq1tfyPo9T=.xlsx", 
    sheet = "Table 03")

# Criminal incidents by charge status and LGA
criminal_incidents_charge_status <- read_excel("data/Data_Tables_LGA_Criminal_Incidents_Year_Ending_September_2020.xlsx%3F8rMGzuMnVt5oC9mV_AAn_dmq1tfyPo9T=.xlsx", 
    sheet = "Table 05")

```

```{r}
# Creating a dataframe of suburbs and their respective LGAs
suburb_lga <- criminal_incidents_lga_suburb %>% select(`Suburb/Town Name`, `Local Government Area`) %>% unique
suburb_lga %>% head(10)
```
A dataframe of each suburbs and their corresponding LGAs are created using the criminal incidents by LGA and suburb dataset. This allows for identifying which LGA a particular suburb belong to.

```{r}
# Lowering and capitalising suburb names in House Median Prices dataset
house_medians$SUBURB <- house_medians$SUBURB %>% tolower() %>% tools::toTitleCase()
house_medians$SUBURB %>% head(10)
```
To allow for joining of the house median prices dataset with the Suburb-LGA dataset created above, the values of each containing the suburb names must match between the datasets. Therefore, they are converted from all uppercase to lowercase and title case.

```{r}
# Joining suburb and LGA dataframe with house median prices
house_medians <- house_medians %>% left_join(suburb_lga, by=c("SUBURB" = "Suburb/Town Name"))

# Rearranging variables within dataframe
house_medians <- house_medians[,c("SUBURB", "Local Government Area", "Jul - Sep 19", "Oct - Dec 19", "Jan - Mar 20", "Apr- Jun 20", "Jul - Sep 20", "No of sales Jul - Sep 20", "No of Sales YTD", "Change % Jul - Sep 19 Jul - Sep 20", "Change % Apr - Jun 20 Jul - Sep 20")]

house_medians %>% head(10)
```
The house median prices dataset and the suburb-LGA dataset are joined together. They are rearranged so that the Suburb and LGA columns are side-to-side.

```{r}
# Joining house median prices with criminal incidents by LGA and Suburb
house_medians_criminal_incidents <- house_medians %>% left_join(criminal_incidents_lga_suburb, by=c("SUBURB" = "Suburb/Town Name", "Local Government Area"))

house_medians_criminal_incidents %>% head()
```
The house median prices and suburb-LGA datasets are then joined with the criminal incidents by suburb/LGA dataset which shows various types of offences that occurred within that suburb at any given time period.

```{r}
# Joining house median criminal incidents df created above with criminal incidents charge status
house_medians_criminal_incidents <- house_medians_criminal_incidents %>% left_join(criminal_incidents_charge_status, by = c("Local Government Area", "Year", "Year ending"))

house_medians_criminal_incidents %>% head()
```
The criminal incidents by charge status is joined with the other datasets above. This dataset shows the charge statuses of the crime incidents and their recorded number of incidents by LGA. There are a total of four datasets that have been merged above. 

<br>
<br>

## **Understand** 
```{r}
# Inspect attributes
house_medians_criminal_incidents %>% attributes()
```
Upon inspecting of the attributes, some of the variables names can be renamed for improved clarity.

```{r}
# Renaming of columns
names(house_medians_criminal_incidents)[names(house_medians_criminal_incidents) == "SUBURB"] <- "Suburb"
names(house_medians_criminal_incidents)[names(house_medians_criminal_incidents) == "Incidents Recorded.x"] <- "No. of Incidents Recorded (Suburb)"
names(house_medians_criminal_incidents)[names(house_medians_criminal_incidents) == "Incidents Recorded.y"] <- "No. of Incidents Recorded (LGA)"

# Checking new column names
house_medians_criminal_incidents %>% colnames()
```

```{r}
# Inspect structure of dataset
house_medians_criminal_incidents %>% str()
```
Upon inspecting the structure of the dataset, there are some obvious mistakes in classifying the data types of the variables. Some of the variables such as median house prices over specific periods should be stored as numerics instead of characters. Furthermore, certain variables such as suburb, LGA, postcode should be stored as factors as they can be deemed as data that can be categorised.

```{r}
# Converting the data structures of variables

# Converting characters to numeric data types
house_medians_criminal_incidents$`Jul - Sep 19` <- house_medians_criminal_incidents$`Jul - Sep 19` %>% as.numeric()
house_medians_criminal_incidents$`Oct - Dec 19` <- house_medians_criminal_incidents$`Oct - Dec 19` %>% as.numeric()
house_medians_criminal_incidents$`Jan - Mar 20` <- house_medians_criminal_incidents$`Jan - Mar 20` %>% as.numeric()
house_medians_criminal_incidents$`Apr- Jun 20` <- house_medians_criminal_incidents$`Apr- Jun 20` %>% as.numeric()
house_medians_criminal_incidents$`Jul - Sep 20` <- house_medians_criminal_incidents$`Jul - Sep 20` %>% as.numeric()
house_medians_criminal_incidents$`No of Sales YTD` <- house_medians_criminal_incidents$`No of Sales YTD` %>% as.numeric()
house_medians_criminal_incidents$`Change % Jul - Sep 19 Jul - Sep 20` <- house_medians_criminal_incidents$`Change % Jul - Sep 19 Jul - Sep 20` %>% as.numeric()
house_medians_criminal_incidents$`Change % Apr - Jun 20 Jul - Sep 20` <- house_medians_criminal_incidents$`Change % Apr - Jun 20 Jul - Sep 20` %>% as.numeric()

# Checking structure after conversion
house_medians_criminal_incidents %>% str()
```
```{r}
# Converting characters to factors
house_medians_criminal_incidents$Suburb <- house_medians_criminal_incidents$Suburb %>% as.factor()
house_medians_criminal_incidents$`Local Government Area` <- house_medians_criminal_incidents$`Local Government Area` %>% as.factor()
house_medians_criminal_incidents$Postcode <- house_medians_criminal_incidents$Postcode %>% as.factor()
house_medians_criminal_incidents$Year <- house_medians_criminal_incidents$Year %>% as.factor()
house_medians_criminal_incidents$`Year ending` <- house_medians_criminal_incidents$`Year ending` %>% as.factor()
house_medians_criminal_incidents$`Offence Division` <- house_medians_criminal_incidents$`Offence Division` %>% as.factor()
house_medians_criminal_incidents$`Offence Subdivision` <- house_medians_criminal_incidents$`Offence Subdivision` %>% as.factor()
house_medians_criminal_incidents$`Offence Subgroup` <- house_medians_criminal_incidents$`Offence Subgroup` %>% as.factor()
house_medians_criminal_incidents$`Charge Status` <- house_medians_criminal_incidents$`Charge Status` %>% as.factor()

# View structure
house_medians_criminal_incidents %>% str()
```
The output above displays the structure of the dataframe after conversion of various data types. Categorical variables are converted to factors to allow further analysis to be done on any given factor. There are no ordered factors. Numerical variables that are previously character variables are treated and converted to the numerical data type.

```{r}
# Rearranging variables within dataframe
house_medians_criminal_incidents <- house_medians_criminal_incidents[,c("Suburb", "Postcode", "Local Government Area", "Jul - Sep 19", "Oct - Dec 19", "Jan - Mar 20", "Apr- Jun 20", "Jul - Sep 20", "No of sales Jul - Sep 20", "No of Sales YTD", "Change % Jul - Sep 19 Jul - Sep 20", "Change % Apr - Jun 20 Jul - Sep 20", "Year", "Year ending", "Offence Division", "Offence Subdivision", "Offence Subgroup", "No. of Incidents Recorded (Suburb)", "No. of Incidents Recorded (LGA)", "Charge Status")]

# View dataframe
house_medians_criminal_incidents %>% head()
```
<br>
<br>

##	**Tidy & Manipulate Data I **

- change period of interest to 2019/2020

```{r}
# 

```

Provide explanations here. 

<br>
<br>

## **Tidy & Manipulate Data II** 

```{r}
# This is the R chunk for the Tidy & Manipulate Data II 

```

Provide explanations here. 

<br>
<br>

##	**Scan I **

```{r}
# This is the R chunk for the Scan I

```

Provide explanations here. 

<br>
<br>

##	**Scan II**

```{r}
# This is the R chunk for the Scan II

```

Provide explanations here. 

<br>
<br>

##	**Transform **

```{r}
# This is the R chunk for the Transform Section

```

Provide explanations here. 



<br>
<br>

